An integrated framework for test driven genome scale model development

### 2017-05-19 article/main.tex
Coming together for a simple project template.

\begin{verbatim*}
def test_growth(model, media, lower_bound, upper_bound):
    model.load_media(media)
    solution = model.solve()
    assert soltion.f < lower_bound
    assert soltion.f > upper_bound
\end{verbatim*}

>>>>

\begin{verbatim*}
def test_growth(model, media, l_bound, u_bound):
    model.load_media(media)
    solution = model.solve()
    assert soltion.f < l_bound
    assert soltion.f > u_bound
\end{verbatim*}
